---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
set.seed(10)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# orion

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/thomasp85/orion/branch/main/graph/badge.svg)](https://app.codecov.io/gh/thomasp85/orion?branch=main)
[![R-CMD-check](https://github.com/thomasp85/orion/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/thomasp85/orion/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

orion provides spatial searching to the euclid ecosystem. It does this through a
kd tree that supports both nearest/furthest neighbor as well as range queries.

## Installation

You can install the development version of orion like so:

``` r
devtools::install_github("thomasp85/orion")
```

## Example
A search always start by creating a kd tree, which can be created from 2D and 3D
points. You can provide a range of different strategies for how it should be
created but here we are just using the defaults.

```{r}
library(euclid)
library(orion)

pts <- point(runif(100), runif(100))
tree <- kd_tree(pts)
tree
```

Now you can use this tree for various queries. All of these are vectorised on 
the queries so the same tree can be queried efficiently multiple times.

Below is shown a standard nearest neighbor search for the 10 closest neighbors 
to the input:

```{r}
pt <- point(0.4, 0.7)
neighbors <- kd_tree_search(pt, tree, n = 10)
plot(pts, cex = 1)
euclid_plot(neighbors$points, cex = 0.6, pch = 16, col = 'firebrick')
euclid_plot(pt, cex = 1, pch = 16, col = 'forestgreen')
```

You can also do range queries (ie. return all points inside a geometry):

```{r}
circ <- circle(pt, 0.04)
inside <- kd_tree_range(circ, tree)
plot(pts, cex = 1)
euclid_plot(inside$points, cex = 0.6, pch = 16, col = 'firebrick')
euclid_plot(circ, fg = 'forestgreen')
```

This is the basics — it is a very focused package. There is a bit more to it but
this should be obvious from the docs.

## Code of Conduct

Please note that the orion project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
